---
title: "Components"
author: "Jumping Rivers"
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r echo=FALSE} 
setnicepar = function(mar=c(3,3,2,1), 
         mgp=c(2,0.4,0), tck=-.01,
         cex.axis=0.9, las=1, mfrow=c(1,1),...) {
  par(mar=mar, 
      mgp=mgp, tck=tck,
      cex.axis=cex.axis, las=las,mfrow=mfrow,...)
}
```


```{r setup}
library(shiny)
library(flexdashboard)
#library(nclRshiny)
library("ggplot2movies")
library(ggplot2)
library(flexdashboard)
data(movies, package="ggplot2movies")
movies = movies[!is.na(movies$budget) & movies$budget > 0,]
top_movies = movies[order(-movies$rating), c("title", "year", "budget", "rating", "Romance", "Action", "Animation"), ]
colnames(top_movies)  = c("Title", "Year", "Budget", "Rating","Romance", "Action", "Animation")
theme_set(theme_bw())


t_m = reactive(top_movies[top_movies[input$movie_type]==1,])
years = reactive(movies[movies$year > 1929 & movies[input$movie_type]==1,])
an = reactive(movies[movies[input$movie_type]==1,])
```


Selections {.sidebar}
===============================


Select the movie genre to display

```{r}
selectInput("movie_type", label = "Movie genre", c("Romance", "Action", "Animation"))
selectInput("mpaa", label = "MPAA", c("R", "PG-13", "PG", "NC-17"))
actionButton("replot", "Plot")
```

Note I've used a global side-bar here.

Tables
===================================== 

Column {.tabset .tabset-fade}
-------------------------------------
### Top 10 movies (static)

```{r}
renderTable({
  t_m_isolate = isolate(t_m())
  input$replot
  t_m_isolate[1:10, 1:4]
})
```

### Top 10 movies (dynamic)

```{r}
DT::renderDataTable({
  t_m_isolate = isolate(t_m())
  input$replot
  DT::datatable(t_m_isolate[,1:4], rownames = FALSE)})
```


Base graphics 
===================================== 

### Rating vs Length

```{r}
renderPlot({
setnicepar()
plot(an()$rating, an()$length, ylab="Length", xlab="Rating", 
      pch=21, bg="steelblue", ylim=c(0, max(an()$length)), 
     xlim=c(1, 10), main=paste0(input$movie_type, " movies"))
grid()
})
```

### Movie Length

```{r}
renderPlot({
  setnicepar()
  hist(an()$length, breaks="fd", col="steelblue", xlab="Movie Length", 
      main="Histogram of movie length", xlim=c(0, max(an()$length)))
  grid()
})
```

htmlwidget and value boxes
===================================== 

Column 1 {data-width=200}
------------------------------------
### Length vs rating

This example makes use of the `plotly` and `ggplot2`. There is also a `valuebox` showing the number
of terrible movies.

```{r}
library(plotly)
renderPlotly({
g = ggplot(an(), aes(length, rating)) + 
  geom_point(size=0.5, aes(text=paste("Film: ", title))) + 
  xlab("Length") + ylab("Rating") + 
  ylim(c(0, 10)) 
ggplotly(g)
})
```

### Value boxes

```{r}
renderValueBox({
  valueBox(sum(an()$rating <3), icon = "ion-videocamera", caption="Movies Rated less than 3", 
         color="red")
})
```

Column 2 {data-width=300}
-------------------------------------

### Movie ratings over number

This example makes use of the `dygraphs` R package. The dygraphs
package provides rich facilities for charting time-series data 
in R. 

```{r}
library(dygraphs)
renderDygraph({
rat_by_year = tapply(years()$rating, years()$year, mean)
x = ts(as.vector(rat_by_year), start=1930)
y = cbind(Rating=x)
dygraph(y, main = "Ratings over the years", 
        ylab = "Ratings", group="Ratings") %>% 
  dyRangeSelector() %>%
   dyOptions(stepPlot = TRUE) %>%
  dySeries("V1", label = "Rating")
})
```

### Number of movies made

```{r}
library(dygraphs)
renderDygraph({
num_by_year = tapply(years()$rating, years()$year, sum)
x = ts(as.vector(num_by_year), start=1930)
y = cbind(Rating=x)
dygraph(y, main = "Number of movies over the years", 
        ylab = "No. of movies",group="Ratings") %>% 
  dyRangeSelector() %>%
   dyOptions(stepPlot = TRUE) %>%
  dySeries("V1", label = "No. of Movies made")
})
```





