---
title: "chapter 3 Exercises"
author: "Jumping Rivers"
output: html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Chapter 3 Exercises}
-->

```{r echo=FALSE, message=FALSE}
library("nclRshiny")
library("flexdashboard")
```

## Exercise 1 (15 minutes)

  1. Open `exercises/chapter3/single_column_fill.Rmd` and Knit. 
    * Add two additional charts to get the following layout
  
        ```{r echo=FALSE, fig.height=2, fig.width=2}
        layout(matrix(c(1:4), 4, 1, byrow = TRUE))
        layout_show(4,2)
        ```
  1. What is the difference between `Column (fill)` and `Column (scroll)`. 
  Hint: create a dashboard with $6$ charts for `fill` and `scroll`
    
  1. Open `exercises/chapter3/row.Rmd`. Recreate the following layouts
  
    *  Layout 1
    
        ```{r echo=FALSE, fig.height=2, fig.width=2}
        layout(matrix(c(1:4), 2, 2, byrow = TRUE))
        layout_show(4,1)
        ```
    *  Layout 2
    
        ```{r echo=FALSE, fig.height=2, fig.width=2}
        layout(matrix(c(1:2, 3, 3, 4:5), 3, 2, byrow = TRUE))
        layout_show(5,1)
        ```

## Exercise 2 (15 minutes)
  
Create the following layouts

  * Layout 1 (use `{data-width=XXX}`)
  
      ```{r echo=FALSE, fig.height=2, fig.width=2}
      layout(matrix(c(1, 1, 2, 3:5), 2, 3, byrow = TRUE))
      layout_show(5,1)
      ```
  * Layout 2 (use `{data-height=XXX}`)
    
      ```{r echo=FALSE, fig.height=2, fig.width=2}
      layout(matrix(c(1, 1, 2,1, 1, 2, 3:5), 3, 3, byrow = TRUE))
      layout_show(5,1)
      ```

## Exercise 3 (30 minutes)

  1. Open the `Multiple columns` `.Rmd` file and knit. 
  Create the following layout.

    ```{r echo=FALSE, fig.height=2, fig.width=2}
    layout(matrix(c(1, 1, 2, 4, 
                    1, 1, 2, 5, 
                    1, 1, 3, 6,
                    1, 1, 3, 7), 4, 4, byrow = TRUE))
    layout_show(7,1)
    ```
  1. Open `chapter3/pages.Rmd`. 
    * Open the vignette `components`
    ```{r eval=FALSE}
    vignette("components", package="nclRshiny")
    ```
    to give you an idea of what is possible. The source code for the vignette is in the file
    `chapter3/components.Rmd`
    *  Create a dashboard with $3$ pages. Add some graphs (perhaps using htmlwidgets) of your own data.
  1. The flexdashboard [documentation](http://rmarkdown.rstudio.com/flexdashboard/using.html#multiple_pages)
  gives more details on pages. Including, 
    * [Orientation](http://rmarkdown.rstudio.com/flexdashboard/using.html#page_orientation)
    * [Navigation](http://rmarkdown.rstudio.com/flexdashboard/using.html#page_navigation)
    * [Links](http://rmarkdown.rstudio.com/flexdashboard/using.html#page_links) and [icons](http://rmarkdown.rstudio.com/flexdashboard/using.html#page_icons)
    
## Exercise 4 (20 minutes)

1. It's easy to create tab panes. 
  * Open `chapter3/tabs.Rmd`. 
  * What does the `.tabset-fade` attribute do?
  * Alter one of your existing layouts and add a tab component
1. Look at my [app](https://bookdown.org/csgillespie/components/) How do you think it was created?
2. Another neat layout is [Storyboard](http://rmarkdown.rstudio.com/flexdashboard/using.html#storyboards)
  * Knit `chapter3/story.Rmd`.
  * Add an additional frame to the storyboard containing a `boxplot` of the simulated data.
  * [Example](https://beta.rstudioconnect.com/jjallaire/htmlwidgets-showcase-storyboard/) from RStudio


