---
title: "Chapter 1 Exercises"
author: "Jumping Rivers"
output: html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Chapter 1 Exercises}
-->
  
```{r echo=FALSE, message=FALSE}
library("nclRshiny")
```

## Exercise 1 (8 minutes)

  * In RStudio, select `File`, then `New Project`. Create a new RStudio project in 
  an empty directory.
  * Run the command `nclRshiny::create_project()`. This should create two directories: `original`
  and `exercises`.
  * Open `exercises/chapter1/rmarkdown1.Rmd`. Click `Knit HTML`
  * Complete the instructions in the file

## Exercise 2 (8 minutes)

  * Open `exercises/chapter1/rmarkdown2.Rmd`. Click `Knit HTML`
  * Complete the instructions in the file
  
## Exercise 3 (15 minutes)

  * Open `exercises/chapter1/rmarkdown3.Rmd`. Click `Knit HTML`
  * We can change how the slides are displayed:
    * Swap `output: ioslides_presentation` to `output:slidy_presentation` to re-knit
    * Install the `reveal.js` package
    ```{r eval=FALSE}
    ## Hope this should work!
    install.packages("revealjs")
    ```
    and change to `output: revealjs::revealjs_presentation`. On my machine, I had to view the
    presentation in a browser on full-screen mode. More details are available at 
    the [RStudio](http://rmarkdown.rstudio.com/revealjs_presentation_format.html) web-page.
  * Change the slides to use your data.
  
  
