---
title: "Chapter 1: Exercise 2"
date: "`r Sys.Date()`"
author: "Jumping Rivers"
output: html_document
---

## Markdown chunk option

For each knitr code chunk option below

1. Experiment with the different options.
2. Re-render the file to see what the option does. If you cannot tell, re-render the file both with and without the code chunk.
3. Describe in your own words what the option does.
4. Use the RStudio's auto complete function; this is accessed via the TAB key.

***

### eval

  * What happens when `eval=TRUE`?
  * What is the default?
```{r eval=FALSE}
colMeans(cars)
1 + 1
```
Description:

***

### results

  * Options for results are `hide`, `markup` and `asis`
  * What is the default?
```{r results = 'asis'}
carmeans = colMeans(cars)
1 + 1
```
Description:

***

###  echo
  * Try `echo=TRUE`. What's the default value for `echo`?

```{r echo = FALSE}
plot(cars)
```
Description:

***

### fig.width and fig.height

When adding multiple arguments to a code chunk, separate the arguments by a comma.

```{r fig.width = 5, fig.height = 4}
plot(cars)
```
Description:

***

### message   

```{r message = FALSE}
f = function(x) {
  message("Thanks")
  return(x)
}
f(10)
```
Description:

***
