---
title: "Why we need observeEvents"
author: "Jumping Rivers"
runtime: shiny
---
### Problem

We have two action buttons. When we click a button, we wish to generate a new plot. 
However, dependencies within `reactive` function are constructed dynamically as the
code is run. In the case below, because `input$unif` is not executed, then it is not
included as a dependency.

```{r echo=FALSE}
actionButton("norm", "Normal")
actionButton("unif", "Uniform")
## Reactive dependencies are dynamic
rv1 = reactive({
  if(input$norm) {
    rnorm(100)
  } else if(input$unif){
    runif(100)
  } else {
    rnorm(100)
  }
})

renderPlot(plot(rv1()))
```


### Solution

Combine `reactiveValues` and `observeEvents`. 
  * `reactiveValues` creates a list of reactive values that you can update in your code
  * You can update the reactive values from inside a call to

```{r echo=FALSE}
rv2 = reactiveValues(data = rnorm(100))

observeEvent(input$norm, {rv2$data = rnorm(100)})
observeEvent(input$unif, {rv2$data = runif(100)})
renderPlot({plot(rv2$data)})
```


#### Further information

  * https://shinydata.wordpress.com/2015/02/02/a-few-things-i-learned-about-shiny-and-reactive-programming/