---
title: "Components"
author: "Jumping Rivers"
output: flexdashboard::flex_dashboard
source_code: embed
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Chapter 3: h - Flexdashboard Components}
-->
```{r setup, include=FALSE}
library(flexdashboard)
library(nclRshiny)
library("ggplot2movies")
library(ggplot2)
library(flexdashboard)
data(movies, package="ggplot2movies")
movies = movies[!is.na(movies$budget) & movies$budget > 0,]
top_movies = movies[order(-movies$rating), c("title", "year", "budget", "rating"), ]
colnames(top_movies)  = c("Title", "Year", "Budget", "Rating")
an = movies[movies$Animation==1,]

theme_set(theme_bw())
```

Standard text can be added at the top of page if you want. You can include sections and bullet points. As well as

  * Equations
  * Static pictures
  * links

To add text within a pane, use the block quote `>`

Tables
===================================== 

Column {.tabset .tabset-fade}
-------------------------------------
### Top 10 movies (static)


```{r}
knitr::kable(top_movies[1:10,], row.names = FALSE)
```

### Top 10 movies (dynamic)

```{r}
DT::datatable(top_movies, rownames = FALSE)
```

Base graphics 
===================================== 

### Animation movies: Rating vs Length

```{r}
setnicepar()
plot(an$rating, an$length, ylab="Length", xlab="Rating", 
      pch=21, bg="steelblue", ylim=c(0, 140), xlim=c(1, 10))
grid()
```

### Animation movies: Length

```{r}
setnicepar()
hist(an$length, breaks="fd", col="steelblue", xlab="Movie Length", 
     main="Histogram of movie length")
```

htmlwidget and value boxes
===================================== 

Column 1 {data-width=200}
------------------------------------
### Length vs rating

This example makes use of the `plotly` and `ggplot2`. There is also a `valuebox` showing the number
of terrible movies.

```{r}
library(plotly)
g = ggplot(movies, aes(length, rating)) + 
  geom_point(size=0.5, aes(text=paste("Film: ", title))) + 
  xlab("Length") + ylab("Rating") + 
  ylim(c(1, 10)) 
ggplotly(g)
```

### Value boxes

```{r}
valueBox(sum(movies$rating <2), icon = "ion-videocamera", caption="Movies Rated less than 2", 
         color="red")
```




Column 2 {data-width=300}
-------------------------------------

### Movie ratings over number

This example makes use of the `dygraphs` R package. The dygraphs
package provides rich facilities for charting time-series data 
in R. 

```{r}
library(dygraphs)
years = movies[movies$year > 1929,]
rat_by_year = tapply(years$rating, years$year, mean)

x = ts(as.vector(rat_by_year), start=1930)
y = cbind(Rating=x)
dygraph(y, main = "Ratings over the years", 
        ylab = "Ratings", group="Ratings") %>% 
  dyRangeSelector() %>%
   dyOptions(stepPlot = TRUE) %>%
  dySeries("V1", label = "Rating")
```

### Number of movies made

```{r}
library(dygraphs)
years = movies[movies$year > 1929,]
num_by_year = tapply(years$rating, years$year, sum)
x = ts(as.vector(num_by_year), start=1930)
y = cbind(Rating=x)
dygraph(y, main = "Number of movies over the years", 
        ylab = "No. of movies",group="Ratings") %>% 
  dyRangeSelector() %>%
   dyOptions(stepPlot = TRUE) %>%
  dySeries("V1", label = "No. of Movies made")

```





